### 2018-03-17 papers.tex
papers.tex: Switch track names for reasons that will become clear as we review later
Add my paper
Add Stefan and Ben's paper

\addtrack
	{Theory}{\textit{Bottles}}
\addpaper
	{Sublinear colorings of 3-colorable graphs in linear time}
	{Thomas Tseng}
	{Keywords: graph coloring, approximation algorithms, analysis of algorithms}
	{SIGBOVIK_2018_paper_3}
	{0cm}
	{}
\addpaper
	{Cubic partitioning of simultaneous antipodal 4-corner-day time spaces}
	{R.\ Welch and G.\ Ray}
	{Keywords: timecube, conspiracy theories, applied mathematics, applied cubism, tuesdays, meridian time, word animals}
	{SIGBOVIK_2018_paper_2}
	{0cm}
	{}
\addpaper
	{Chess circuits}
	{Ross Dempsey, Sydney Timmerman, and Karl Osterbauer}
	{Keywords: chess, logic, boolean circuits}
	{SIGBOVIK_2018_paper_22}
	{2cm}
	{}

@@

\addtrack
	{Ayyy Eye}{\textit{Open Your Third Eye}}
\addpaper
	{PSYCHO:\ PerSonalitY CHaracterizatiOn of artificial intelligence}
	{Achal Dave and Rohit Girdhar}
	{Keywords: interpretability, psychology, deep learning, artificial intelligence, rorschach}
	{SIGBOVIK_2018_paper_8}
	{0cm}
	{}
\addpaper
	{The NUGGET non-linear piecewise activation}
	{Stephen Merity}
	{Keywords: deep learning, neural networks, nugget, nuggets, chicken nuggets, smart}
	{SIGBOVIK_2018_paper_10}
	{0cm}
	{}
\addpaper
	{Substitute teacher networks:\ Learning with almost no supervision}
	{Samuel Albanie, James Thewlis, and Jo\~ao F.\ Henriques}
	{Keywords: substitute, teacher, networks}
	{SIGBOVIK_2018_paper_28}
	{1cm}
	{}

@@

\addtrack
	{Art}{\textit{The Way They Fly}}
\addpaper
	{Automating art snobbiness:\ Dead duck or phoenix?}
	{Dion Ysus and Oscar I.\ Hernandez}
	{Keywords: automation, art, elite, 1337 dankster, cicada 3301, de Bruijn sequence}
	{SIGBOVIK_2018_paper_14}
	{0cm}
	{}
\addpaper
	{Toward a historically faithful performance of the piano works of Anton\'in Qwe\v{r}t\'y}
	{William Gunther and Brian Kell}
	{Keywords: G-flat major, F-sharp minor, A-flat harmonic major $\flat$6 $\flat$5, G-sharp harmonic major $\flat$5}
	{SIGBOVIK_2018_paper_21}
	{0cm}
	{}
\addpaper
	{WordTeX:\ A WYSIPCTWOTCG typesetting tool}
	{Tom Wildenhain}
	{Keywords: Word, Microsoft Word, LaTeX, WordTeX}
	{SIGBOVIK_2018_paper_12}
	{0cm}
	{}

@@

\addtrack
	{Systems}{\textit{Wheel}}
\addpaper
	{The fluint8 software integer library}
	{Jim McCann and Tom Murphy VII}
	{Keywords: uint8\_t, float, binary32, ieee754}
	{SIGBOVIK_2018_paper_18}
	{0cm}
	{}
\addpaper
	{mallocd:\ designing a garbage-free nosql data store}
	{igor}
	{Keywords: state-of-the-art, in-memory, garbage-free, cloud-native, nosql, bare metal, containerless, micro-service, data store}
	{SIGBOVIK_2018_paper_4}
	{0cm}
	{}

>>>>

\addtrack
	{Theory}{\textit{Bottles}}
\addpaper
	{Sublinear colorings of 3-colorable graphs in linear time}
	{Thomas Tseng}
	{Keywords: graph coloring, approximation algorithms, analysis of algorithms}
	{SIGBOVIK_2018_paper_3}
	{0cm}
	{}
\addpaper
	{Cubic partitioning of simultaneous antipodal 4-corner-day time spaces}
	{R.\ Welch and G.\ Ray}
	{Keywords: timecube, conspiracy theories, applied mathematics, applied cubism, tuesdays, meridian time, word animals}
	{SIGBOVIK_2018_paper_2}
	{0cm}
	{}
\addpaper
	{Construction of Eulerian trails in large graphs}
	{Stefan Muller and Ben Blum}
	{Keywords: walk, Eulerian trail, large graph}
	{SIGBOVIK_2018_paper_29}
	{0cm}
	{}
\addpaper
	{Chess circuits}
	{Ross Dempsey, Sydney Timmerman, and Karl Osterbauer}
	{Keywords: chess, logic, boolean circuits}
	{SIGBOVIK_2018_paper_22}
	{2cm}
	{}

@@

\addtrack
	{Ayyy Eye}{\textit{Afterimage of a Crimson Eye}}
\addpaper
	{PSYCHO:\ PerSonalitY CHaracterizatiOn of artificial intelligence}
	{Achal Dave and Rohit Girdhar}
	{Keywords: interpretability, psychology, deep learning, artificial intelligence, rorschach}
	{SIGBOVIK_2018_paper_8}
	{0cm}
	{}
\addpaper
	{The NUGGET non-linear piecewise activation}
	{Stephen Merity}
	{Keywords: deep learning, neural networks, nugget, nuggets, chicken nuggets, smart}
	{SIGBOVIK_2018_paper_10}
	{0cm}
	{}
\addpaper
	{Substitute teacher networks:\ Learning with almost no supervision}
	{Samuel Albanie, James Thewlis, and Jo\~ao F.\ Henriques}
	{Keywords: substitute, teacher, networks}
	{SIGBOVIK_2018_paper_28}
	{1cm}
	{}

@@

\addtrack
	{Art}{\textit{Open Your Third Eye}}
\addpaper
	{Automating art snobbiness:\ Dead duck or phoenix?}
	{Dion Ysus and Oscar I.\ Hernandez}
	{Keywords: automation, art, elite, 1337 dankster, cicada 3301, de Bruijn sequence}
	{SIGBOVIK_2018_paper_14}
	{0cm}
	{}
\addpaper
	{Toward a historically faithful performance of the piano works of Anton\'in Qwe\v{r}t\'y}
	{William Gunther and Brian Kell}
	{Keywords: G-flat major, F-sharp minor, A-flat harmonic major $\flat$6 $\flat$5, G-sharp harmonic major $\flat$5}
	{SIGBOVIK_2018_paper_21}
	{0cm}
	{}
\addpaper
	{WordTeX:\ A WYSIPCTWOTCG typesetting tool}
	{Tom Wildenhain}
	{Keywords: Word, Microsoft Word, LaTeX, WordTeX}
	{SIGBOVIK_2018_paper_12}
	{0cm}
	{}

@@

\addtrack
	{Systems}{\textit{Wheel}}
\addpaper
	{The fluint8 software integer library}
	{Jim McCann and Tom Murphy VII}
	{Keywords: uint8\_t, float, binary32, ieee754}
	{SIGBOVIK_2018_paper_18}
	{0cm}
	{}
\addpaper
	{mallocd:\ designing a garbage-free nosql data store}
	{igor}
	{Keywords: state-of-the-art, in-memory, garbage-free, cloud-native, nosql, bare metal, containerless, micro-service, data store}
	{SIGBOVIK_2018_paper_4}
	{0cm}
	{}
\addpaper
	{A survey of hardware multithreading}
	{Sol Boucher}
	{Keywords: bend, the, kneedle}
	{SIGBOVIK_2018_paper_EasierChair}
	{0cm}
	{}
